### 2019-11-12 report/05-stability.Rmd
Add synchrony method for trophic species + plot method for species biomass dynamic

# Results

## Network description

```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
# Get network metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)

cor_avg <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med"))) %>%
  cor()
#knitr::kable(cor_avg)
as.data.frame(round(cor_avg,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
cor_cv <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("cv"))) %>%
  cor()
as.data.frame(round(cor_cv,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r}
library(ade4)
library(factoextra)

net_ind <- temporal_network_metrics %>%
  left_join(select(temporal_community_metrics, station, richness_med)) %>%
  select_at(vars(dplyr::matches("med")))

res.pca <- dudi.pca(na.omit(net_ind),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)
eig_plot <- fviz_eig(res.pca)
```

```{r}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})

temp_plot <- plot_grid(plotlist = pca_plot)
plot_grid(temp_plot, eig_plot)
```

### Look at some network temporal series

Let's look at network that have particular network properties.

```{r}
myload(network_analysis, dir = mypath("data", "species"))
myload(op_analysis, metaweb_analysis, dir = data_common)
meta <- metaweb_analysis; rm(metaweb_analysis)

net <- network_analysis %>%
  dplyr::select(opcod, network) %>%
  unnest() %>%
  left_join(., dplyr::select(op_analysis, opcod, station, date)) 
```

```{r}
station_high_low_modularity <- temporal_network_metrics %>%
  arrange(desc(modularity_med)) %>%
  slice(c(1, n())) %>%
  select(station) %>%
  unlist
names(station_high_low_modularity) <- c("high", "low") 
```

```{r tmp-net-h-mod, fig.cap = "Station with the highest modularity (median)."}
# High modularity
net_ex <- filter(net, station == station_high_low_modularity["high"])

my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```
```{r tmp-net-l-mod, fig.cap = "Station with the lowest modularity (median)."}
# Low modularity
net_ex <- filter(net, station == station_high_low_modularity["low"])
my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```

```{r}
station_high_low_nestedness <- temporal_network_metrics %>%
  arrange(desc(nestedness_med)) %>%
  slice(c(1, n())) %>%
  select(station) %>%
  unlist
names(station_high_low_nestedness) <- c("high", "low") 
```
```{r tmp-net-h-nest, fig.cap = "Station with the highest nestedness (median)."}
# high nestedness
net_ex <- filter(net, station == station_high_low_nestedness["high"])
my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```

```{r tmp-net-l-nest, fig.cap = "Station with the lowest nestedness (median)."}
# low nestedness
net_ex <- filter(net, station == station_high_low_nestedness["low"])
my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```

## Productivity

@@

@@

@@

```{r stab-comp, fig.cap = "Link between biomass stability by trophic group and total species richness (median)"}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
net_troph_group <- temporal_network_metrics %>% 
  unnest(troph_group) %>%
  mutate(troph_group = as.factor(troph_group))
net_troph_group %<>%
  select_at(vars(dplyr::matches("_med|stab|station|troph_group"))) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", ""))
p <- ggplot(net_troph_group, aes(y = biomass_stab, x = values, color = troph_group)) +
  geom_point() +
  ggplot2::scale_fill_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    ) +
  facet_wrap(~metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "network_med",
    y = "biomass_stab"
  )
p
```

@@

```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median)"}
net_troph_group <- temporal_network_metrics %>% 
  select(station, troph_group) %>%
  unnest() %>%
  filter(!is.na(troph_group)) %>%
  mutate(troph_group = as.factor(troph_group))
plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = richness_avg)) +
  geom_point() +
  facet_grid(cols = vars(troph_group)) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "richness_avg",
    y = "biomass_stab"
  )
plot_stab_richness_troph_group
```

One hypothesis to explain this opposite pattern might be a disequilibrium
between the two compartment. We can imagine that each compartment can
destabilize each other according to the part of the total biomass of total
species richness that there are in each of them. The figure
\@ref(fig:stab-comp-ratio) showed that the biomass stability of the medium
compartment decreased with the increase of biomass and species number ratio in
the high compartment and we observed the reverse for the high trophic
compartment.

@@

```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level"}
ratio_sp <- net_troph_group %>%
  select(station, troph_group, richness_avg) %>%
  spread(troph_group, richness_avg) %>%
  mutate(sp_h_m = `3` / (`3` + `2`)) %>%
  select(station, sp_h_m)

@@

net_troph_group <- temporal_network_metrics %>%
  left_join(ratio_sp, by = "station") %>%
  left_join(ratio_bm, by = "station") %>%
  select(station, troph_group, sp_h_m, bm_h_m) %>%
  unnest() %>%
  filter(!is.na(troph_group), troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  gather(ratio_troph, value, sp_h_m, bm_h_m)

@@

## Pressure

## SEM

### All

### By basin

>>>>

@@

```{r}
myload(temporal_network_metrics, dir = mypath("data", "cl~/Documents/post-these/mnhn/fishcom/report/index.Rmdasses"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, op_analysis, dir = data_common)
```

@@

```{r}
myload(network_analysis, dir = mypath("data", "classes"))
test <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
test2 <- get_sync_cv_mat(com_analysis = test, op_analysis = op_analysis)

# TODO: Plot for the five stations the most and the less stable:
plot_dyn_sp_biomass(sync = test2, station = 122, .log = TRUE)
plot_dyn_sp_biomass(sync = test2, station = 21877, .log = TRUE)
```

```{r}
high_div_station <- temporal_community_metrics %>%
  arrange(desc(richness_med)) %>%
  slice(1: 5) %>%
  select(station) %>%
  unlist
```

```{r tmp-richest, fig.dim = c(10, 7), fig.cap = "The five highest rich community."}
label_stab <- filter(temporal_community_metrics,
  station %in% high_div_station) %>%
mutate(
  x_pos = ymd_hms("2005-01-01T15:00:00"),
  x_pos = as.Date(x_pos),
  y_pos = 50000,
  text = paste0("Stability: ", round(biomass_stab,2)),
)
ggplot(filter(community_metrics, station %in% high_div_station),
  aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  geom_text(data = label_stab, aes(x = x_pos, y = y_pos, label =
      text), size = 6) +
  facet_wrap( ~ station) + 
  labs(y = "Biomass (g)", x = "Date")
```

```{r}
myload(network_analysis, network_metrics, dir = dest_dir)
high_div_troph_group <- network_metrics %>%
  select(opcod, troph_group) %>%
  unnest() %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  left_join(select(op_analysis, opcod, station, date)) %>%
  filter(station %in% high_div_station)
```

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group,
  aes(y = nbnode, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = label_stab,
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label =
      text), size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The five richest station",
  y = "Fish species richness", x = "Date")
```

```{r}
highest_div_grp_3_station <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group == 3) %>%
  arrange(desc(richness_avg)) %>%
  slice(1:12) %>%
  select(station) %>%
  unlist()
high_div_troph_group_3 <- network_metrics %>%
  select(opcod, troph_group) %>%
  unnest() %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  left_join(select(op_analysis, opcod, station, date)) %>%
  filter(station %in% highest_div_grp_3_station)
```

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Fish species richness", x = "Date")
```

@@

```{r stab-comp, fig.cap = "Link between biomass stability by trophic group and total species richness (median)"}
net_troph_group <- temporal_network_metrics_classes %>% 
  unnest(troph_group) %>%
  mutate(troph_group = as.factor(troph_group))
net_troph_group %<>%
  select_at(vars(dplyr::matches("_med|stab|station|troph_group"))) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", ""))
p <- ggplot(net_troph_group, aes(y = biomass_stab, x = values, color = troph_group)) +
  geom_point() +
  ggplot2::scale_fill_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    ) +
  facet_wrap(~metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "network_med",
    y = "biomass_stab"
  )
p
```

@@

```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median). (Classes network)"}
net_troph_group <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest() %>%
  filter(!is.na(troph_group)) %>%
  mutate(troph_group = as.factor(troph_group))
plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = richness_avg)) +
  geom_point() +
  facet_grid(cols = vars(troph_group)) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "richness_avg",
    y = "biomass_stab"
  )
plot_stab_richness_troph_group
```

One hypothesis to explain this opposite pattern might be a disequilibrium
between the two compartment. We can imagine that each compartment can
destabilize each other according to the part of the total biomass of total
species richness that there are in each of them. The figure
\@ref(fig:stab-comp-ratio) showed that the biomass stability of the medium
compartment decreased with the increase of biomass and species number ratio in
the high compartment and we observed the reverse for the high trophic
compartment. It indicates that a trophic compartment is more stable when their
relative biomass increases.

@@

```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level (classes network) for the medium and high trophic group (resp. left and right panels)."}
ratio_sp <- net_troph_group %>%
  select(station, troph_group, richness_avg) %>%
  spread(troph_group, richness_avg) %>%
  mutate(sp_h_m = `3` / (`3` + `2`)) %>%
  select(station, sp_h_m)

@@

net_troph_group <- temporal_network_metrics_classes %>%
  left_join(ratio_sp, by = "station") %>%
  left_join(ratio_bm, by = "station") %>%
  select(station, troph_group, sp_h_m, bm_h_m) %>%
  unnest() %>%
  filter(!is.na(troph_group), troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  gather(ratio_troph, value, sp_h_m, bm_h_m)

@@
